Adaptive Approximation for Multivariate Linear Problems \\ with Inputs Lying in a Cone

### 2018-11-03 RICAM2018NovTalk.tex

\vspace{-5ex}
How might you construct an adaptive algorithm if you insist on using \alert{balls}?

\vspace{-2ex}
\begin{description}
    \item[Step 1] Start with a default radius $\rho$, and assume input $f \in \cb_{\rho}$

    \item[Step 2] Choose $n$ large enough so that

>>>>

\vspace{-5ex}
How might you construct an \only<2>{\alert{adaptive}} algorithm if you insist on using \alert{balls}?

\vspace{-2ex}
\begin{description}
    \item[Step 1] Pick with a default radius $\rho$, and \alert{assume} input $f \in \cb_{\rho}$

    \item[Step 2] Choose $n$ \alert{large enough} so that
